---
title: "Week4-Homework 3"
author: "Hakeoung Hannah Lee"
date: "2022-09-14"
output: html_document
---

```{r setup}
#library(tidytuesdayR)
library(tidyverse)
library(ggplot2)
library(scales)
library(ggthemes)
```

```{r load data}
tuesdata <- tidytuesdayR::tt_load('2021-03-02')
youtube <- tuesdata$youtube
```
```{r glimpse-data}
glimpse(youtube)
```
```{r check brand}
table(youtube$brand)
table(youtube$year)
```


```{r correction}
sb <- youtube %>%
  mutate(brand = recode(brand, "Hynudai" = "Hyundai"))
```

```{r}
sb_brand <- sb %>%
  group_by(brand) %>%
  filter(brand == c("Kia", "Hyundai", "Toyota")) %>%
  summarize(Funny = mean(funny),
            Show_Product_Quick = mean(show_product_quickly),
            Patriotic = mean(patriotic),
            Celebrity = mean(celebrity),
            Danger = mean(danger),
            Animals = mean(animals),
            Sexuality = mean(use_sex),
            Count = n()) 
```

```{r}
sb_brand2 <- sb_brand %>%
  pivot_longer(2:8, names_to = 'Strategy') %>%
  mutate(Strategy = fct_reorder(Strategy, desc(value))) %>%
  ggplot(aes(Strategy, value, fill = Strategy)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  coord_polar() +
  scale_y_continuous(labels = percent) +
  facet_wrap(~brand) +
  theme_gray() +
  scale_color_hue() +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 7),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10, face = "bold"),
        legend.position = 'right',        
        plot.title = element_text(face = "bold")
        ) +
  labs(fill = 'Strategy',
       title = 'Suberbowl Ads by Three Major Car Brands (2000-2020)',
       subtitle = 'How do Hyundai, Kia, and Toyota use different advertising strategies? \n \n', caption = "\n @Hakeoung Hannah Lee | Source: 2021-03-02 tidytuesday")

plot(sb_brand2)
```

Using the 2021-03-02 tidytuesday Superbowl data, I examined how three major automobile manufactures (Hyundai, Kia, and Toyota) employed distinct advertising strategies over the 2000-2020 Superbowls. I focused on each logical strategy variable (funny, show product quickly, patriotic, celebrity, danger, animals, use sexuality) and the mean value of each variable to generate percentage plots. I discovered that each of the three big automobile manufacturers used a unique advertising strategy. Hyundai highlights the fun aspect the most, whereas Kia highlights celebrity the most, and Toyota uses strategies of quickly showing product and including fun aspect the most.